A New Method of Modelling Tuneable Lasers with Functional Composition

### 2019-07-12 Thesis/Appendices/Asymptotics.tex
Finished corrections

% !TeX root = ../Thesis.tex
%\chapter{Asymptotic Expansions of the Variance}
%\label{chap:asymp}
We shall investigate the nature of the solution to \eqref{eq:var} both when $s \rightarrow 0$ (a very short CFBG), as well as when $s \rightarrow \infty$ (a very long CFBG). For ease of notation, \eqref{eq:var} is rewritten as
\begin{align}
\label{eq:asymp}
\frac{1}{4} x^4 = \eps \left( -x^3 + 5x^2 - 8x + 4 \right),
\end{align}
where $x = \sigma^2$, $\eps = s^4$, and $\eps \rightarrow 0$. Additionally, suppose $x$ can be expanded as a power series in $\eps$:
\begin{align}
\label{eq:series}
x = x_0 + x_1 \eps^\alpha + x_2 \eps^\beta + \cdots
\end{align}
with $0 < \alpha < \beta$. Then, expanding \eqref{eq:asymp} using \eqref{eq:series} and collecting terms, at $\bigO{1}$,
\begin{align*}
\frac{1}{4} x_0^4 = 0,
\end{align*}
and so, $x_0 = 0$. Knowing this, we consider how to balance
\begin{align*}
\frac{1}{4} x_1^4 \eps^{4\alpha} = \eps \left( -x_1^3 \eps^{3\alpha} + 5x_1^2 \eps^{2\alpha} - 8x_1 \eps^\alpha + 4 \right).
\end{align*}
In order to have dominant balance it must be that the left hand side balances with the final term of the right hand side, that is, $4\alpha = 1$, or $\alpha = \frac{1}{4}$. Therefore, at $\bigO{\eps}$ $x_1^4 = 16$, or
\begin{align*}
(x_1 - 2)(x_1 + 2)(x_1^2 + 4) &= 0,
\end{align*}
and so, $x_1 = \pm 2, \, \pm 2 i$. However, we wish $x$ to be positive and real---recall that $x = \sigma^2$---thus, we take $x_1 = 2$. Now, the next lowest order of the left hand side must be $\eps^{3\alpha + \beta} = \eps^{3/4 + \beta}$. As with the previous iteration, this must balance with the lowest order term of the $8x$. Hence, $\frac{3}{4} + \beta = 1 + \alpha = \frac{5}{4}$, thus, $\beta = \frac{1}{2}$. Now, at $\bigO{\eps^{5/4}}$,
\begin{align*}
\frac{1}{4} 4 x_1^3 x_2 &= -8x_1,
\end{align*}
and with the choice of $x_1$, $x_2 = 2$. Combining these results gives $x = 2 \eps^{1/4} - 2 \eps^{1/2} + \bigO{\eps^{3/4}}$, or $\sigma^2 = 2 s \left( 1 - s \right) + \bigO{s^3}$,
this is shown in Figure \ref{fig:lims0}. \\
\begin{figure}[tbp]
\input{./Figures/Lim_s_0}
\caption{Asymptotic expansion of the variance as $s \rightarrow 0$.}
\label{fig:lims0}
\end{figure}

We shall now consider the other limit, when $s \rightarrow \infty$. Using a similar substitution we instead write \eqref{eq:var} as
\begin{align}
\label{eq:asymp2}
\frac{1}{4} \eps x^4 = -x^3 + 5x^2 - 8x + 4,
\end{align}
where $x = \sigma^2$, and $\eps = s^{-4}$ instead so we still have $\eps \rightarrow 0$. Furthermore, we must make a correction to the series expansion:
\begin{align}
\label{eq:series2}
x = \eps^{-\xi} \left( x_0 + x_1 \eps^\alpha + x_2 \eps^\beta + \cdots \right).
\end{align}
The reason for this is because the equation is now singular---when $\eps=0$ the equation transforms from a quartic to a cubic, losing a root. As with before, we obtain dominant balance when the quartic term balances with the cubic term which occurs when $1 - 4 \xi = -3 \xi$, or $\xi = 1$. Then to $\bigO{\eps^{-3}}$, expression \eqref{eq:asymp2} gives
\begin{align*}
x_0^3 (x_0 + 4) &= 0,
\end{align*}
we shall choose $x_0 = 0$---since $x \geq 0$. Continuing, we obtain a dominant balance when $\alpha = 1$. So the next condition occurs at $\bigO{1}$ where
\begin{align*}
0 = -x_1^3 + 5x_1^2 - 8x_1 + 4 = -(x_1 - 1)(x_1 - 2)^2,
\end{align*}
so either $x_1 = 1$ or $x_1 = 2$, we shall see in the next step that we can eliminate one of these. The next term obtains dominant balance when the left hand side balances with the linear term of the right hand side, that is, when $\beta = 2$. Now at $\bigO{\eps}$,
\begin{align*}
\frac{1}{4} x_1^4 = -3x_1^2 x_2 + 5\cdot2 x_1 x_2 - 8x_2 = -x_2 (3x_1 - 4)(x_1 - 2),
\end{align*}
where again, the coefficients come from the binomial expansions. From this it is clear that $x_2$ is unique provided $x_1 \ne 2$ and
\begin{align*}
x_2 &= \frac{-x_1^4}{4(3x_1 - 4)(x_1 - 2)}.
\end{align*}
Thus, $x_1 = 1$, $x_2 = -\frac{1}{4}$, and
\begin{align*}
x = 1 - \frac{1}{4} \eps + x_2 \eps^{\gamma - 1} + \cdots.
\end{align*}
Expanding one final term we find $\gamma = 3$, and to $\bigO{\eps^2}$,
\begin{align*}
\frac{1}{4} 4x_2 x_1^3 &= -(3x_3 x_1^2 + 3x_2^2 x_1) + 5(2x_3 x_1 + x_2^2) - 8x_3.
\end{align*}
Knowing the values of $x_1$, and $x_2$ this is simply an arithmetical calculation yielding $x_3 = \frac{3}{8}$. Finally,
\begin{align*}
x &= 1 - \frac{1}{4}\eps + \frac{3}{8}\eps^2 + \bigO{\eps^3},
\end{align*}
or,
\begin{align*}
\sigma^2 &= 1 - \frac{1}{4s^4} + \frac{3}{8s^8} + \bigO{s^{-12}}
\end{align*}
this approximation is shown in Figure \ref{fig:limsinfty}. \\
\begin{figure}[tbp]
\input{./Figures/Lim_s_Infty}
\caption{Asymptotic expansion of the variance as $s \rightarrow \infty$.}
\label{fig:limsinfty}
\end{figure}

In conclusion, the asymptotic expansions of the observables are
\begin{align*}
\sigma^2 &=
\begin{cases*}
2s(1 - s) + \bigO{s^3} & $s \rightarrow 0$ \\
1 - \frac{1}{4s^4} + \frac{3}{8s^8} + \bigO{s^{-12}} & $s \rightarrow \infty$
\end{cases*}
& C &=
\begin{cases*}
1 - s + \frac{1}{2}s^2 + \bigO{s^3} & $s \rightarrow 0$ \\
\frac{1}{2s^2} - \frac{3}{8s^6} + \bigO{s^{-10}} & $s \rightarrow \infty$
\end{cases*} \\
\frac{C}{\sigma^2} &=
\begin{cases*}
\frac{1}{2s} - \frac{1}{8}s + \bigO{s^3} & $s \rightarrow 0$ \\
\frac{1}{2s^2} - \frac{1}{4s^6} + \bigO{s^{-10}} & $s \rightarrow \infty$
\end{cases*}
& \zeta &=
\begin{cases*}
1 - \frac{1}{2}s + \frac{1}{8}s^2 + \bigO{s^3} & $s \rightarrow 0$ \\
\frac{1}{4^{1/4}s} - \frac{3 \cdot 4^{3/4}}{32 s^5} + \bigO{s^{-9}} & $s \rightarrow \infty$.
\end{cases*}
\end{align*}
The general form of these is as expected. When $s \rightarrow 0$, we effectively remove the CFBG from the cavity. This causes the pulse to be perpetually modulated, and so, the pulse approaches a $\delta$ function, and therefore, $\sigma^2 \rightarrow 0$. Moreover, since $\zeta$ is the ratio of the amplitude of the pulse before and after dispersion, $\zeta \rightarrow 1$. In the opposite extreme, $s \rightarrow \infty$, we have an incredibly long / powerful CFBG---this causes the pulse to broaden greatly, while conserving its energy. Because of this, the variance approaches unity because the shape is entirely determined by the modulation function. Additionally, $\zeta \rightarrow 0$ because the pulse becomes infinitely wide, and thus, the amplitude becomes infinitesimally small. Finally, because of the expansive nature, the chirp approaches zero because any chirp will be inflated away. \\

>>>>

% !TeX root = ../Thesis.tex
%\chapter{Asymptotic Expansions of the Variance}
%\label{chap:asymp}
We shall investigate the nature of the solution to \eqref{eq:var} both when $s \rightarrow 0$ (a very short \gls{cfbg}), as well as when $s \rightarrow \infty$ (a very long \gls{cfbg}). For ease of notation, \eqref{eq:var} is rewritten as
\begin{align}
\label{eq:asymp}
\frac{1}{4} x^4 = - \eps (x - 1)(x - 2)^2,
\end{align}
where $x = \sigma^2$, $\eps = s^4$, and $\eps \rightarrow 0$. Figure \ref{fig:asympt} shows \eqref{eq:asymp}. Additionally, suppose $x$ can be expanded as a power series in $\eps$:
\begin{align}
\label{eq:series}
x = x_0 + x_1 \eps^\alpha + x_2 \eps^\beta + \cdots
\end{align}
with $0 < \alpha < \beta$. Then, expanding \eqref{eq:asymp} using \eqref{eq:series} and collecting terms, at $\bigO{1}$,
\begin{align*}
\frac{1}{4} x_0^4 = 0,
\end{align*}
and so, $x_0 = 0$. Knowing this, we consider how to balance
\begin{align*}
\frac{1}{4} x_1^4 \eps^{4\alpha} = \eps \left( -x_1^3 \eps^{3\alpha} + 5x_1^2 \eps^{2\alpha} - 8x_1 \eps^\alpha + 4 \right).
\end{align*}
In order to have dominant balance it must be that the left hand side balances with the final term of the right hand side, that is, $4\alpha = 1$, or $\alpha = \frac{1}{4}$. Therefore, at $\bigO{\eps}$ $x_1^4 = 16$, or
\begin{align*}
(x_1 - 2)(x_1 + 2)(x_1^2 + 4) &= 0,
\end{align*}
and so, $x_1 = \pm 2, \, \pm 2 i$. However, we require $x$ to be positive and real---recall that $x = \sigma^2$---thus, we take $x_1 = 2$. Now, the next lowest order of the left hand side must be $\eps^{3\alpha + \beta} = \eps^{3/4 + \beta}$. As with the previous iteration, this must balance with the lowest order term of the $8x$. Hence, $\frac{3}{4} + \beta = 1 + \alpha = \frac{5}{4}$, thus, $\beta = \frac{1}{2}$. Now, at $\bigO{\eps^{5/4}}$,
\begin{align*}
\frac{1}{4} 4 x_1^3 x_2 &= -8x_1,
\end{align*}
and with the choice of $x_1$, $x_2 = 2$. Combining these results gives $x = 2 \eps^{1/4} - 2 \eps^{1/2} + \bigO{\eps^{3/4}}$, or $\sigma^2 = 2 s \left( 1 - s \right) + \bigO{s^3}$,
this is shown in Figure \ref{fig:lims0}. The choice $\eps = s^4$ was for convenience, but in retrospect, $\eps = s$ yields a cleaner, but identical, solution. \\
\begin{figure}[tbp]
\input{./Figures/Lim_s_0}
\caption[Asymptotic expansion of the variance as the dispersion parameter approaches 0.]{Asymptotic expansion of the variance as the dispersion parameter, $s$, approaches $0$.}
\label{fig:lims0}
\end{figure}

We shall now consider the other limit, when the dispersion parameter, $s$, approaches $\infty$. Using a similar substitution we instead write \eqref{eq:var} as
\begin{align}
\label{eq:asymp2}
\frac{1}{4} \eps x^4 = -x^3 + 5x^2 - 8x + 4,
\end{align}
where $x = \sigma^2$, and $\eps = s^{-4}$ instead so we still have $\eps \rightarrow 0$, this is also shown in Figure~\ref{fig:asympt}. Furthermore, we must make a correction to the series expansion:
\begin{align}
\label{eq:series2}
x = \eps^{-\xi} \left( x_0 + x_1 \eps^\alpha + x_2 \eps^\beta + \cdots \right).
\end{align}
The reason for this is because the equation is now singular---when $\eps=0$ the equation transforms from a quartic to a cubic, losing a root. As with before, we obtain dominant balance when the quartic term balances with the cubic term which occurs when $1 - 4 \xi = -3 \xi$, or $\xi = 1$. Then to $\bigO{\eps^{-3}}$, expression \eqref{eq:asymp2} gives
\begin{align*}
x_0^3 (x_0 + 4) &= 0.
\end{align*}
The non-trivial solution $x_0 = -4$ gives rise to a boundary layer structure. However, this is unphysical because $x \geq 0$, leaving $x_0^3 = 0$, so this singular perturbation does not generate the boundary layer expected. Therefore, \eqref{eq:series2} reduces to a regular perturbation problem, and $\alpha$ must equal 1. The next condition occurs at $\bigO{1}$ where
\begin{align*}
0 = -x_1^3 + 5x_1^2 - 8x_1 + 4 = -(x_1 - 1)(x_1 - 2)^2,
\end{align*}
so either $x_1 = 1$ or $x_1 = 2$. The next term obtains dominant balance when the left hand side balances with the linear term of the right hand side, that is, when $\beta = 2$ provided\footnote{In the case of $x_1 = 2$ we find $\beta = \frac{3}{2}$ which leads to complex roots.} $x_1 \ne 2$. Now at $\bigO{\eps}$,
\begin{align*}
\frac{1}{4} x_1^4 = -3x_1^2 x_2 + 5\cdot2 x_1 x_2 - 8x_2 = -x_2 (3x_1 - 4)(x_1 - 2),
\end{align*}
where again, the coefficients come from the binomial expansions. From this it is clear that
\begin{align*}
x_2 &= \frac{-x_1^4}{4(3x_1 - 4)(x_1 - 2)}.
\end{align*}
Thus, $x_1 = 1$, $x_2 = -\frac{1}{4}$, and
\begin{align*}
x = 1 - \frac{1}{4} \eps + x_2 \eps^{\gamma - 1} + \cdots.
\end{align*}
Expanding one final term we find $\gamma = 3$, and to $\bigO{\eps^2}$,
\begin{align*}
\frac{1}{4} 4x_2 x_1^3 &= -(3x_3 x_1^2 + 3x_2^2 x_1) + 5(2x_3 x_1 + x_2^2) - 8x_3.
\end{align*}
Knowing the values of $x_1$, and $x_2$ this is simply an arithmetical calculation yielding $x_3 = \frac{3}{8}$. Finally,
\begin{align*}
x &= 1 - \frac{1}{4}\eps + \frac{3}{8}\eps^2 + \bigO{\eps^3},
\end{align*}
or,
\begin{align*}
\sigma^2 &= 1 - \frac{1}{4s^4} + \frac{3}{8s^8} + \bigO{s^{-12}}
\end{align*}
this approximation is shown in Figure \ref{fig:limsinfty}. \\
\begin{figure}[tbp]
\input{./Figures/Lim_s_Infty}
\caption[Asymptotic expansion of the variance as the dispersion parameter approaches $\infty$.]{Asymptotic expansion of the variance as the dispersion parameter, $s$, approaches $\infty$.}
\label{fig:limsinfty}
\end{figure}

In conclusion, the asymptotic expansions of the observables are
\begin{equation}
\begin{aligned}
\sigma^2 &=
\begin{cases*}
2s(1 - s) + \bigO{s^3} & $s \rightarrow 0$ \\
1 - \frac{1}{4s^4} + \frac{3}{8s^8} + \bigO{s^{-12}} & $s \rightarrow \infty$
\end{cases*}
& C &=
\begin{cases*}
1 - s + \frac{1}{2}s^2 + \bigO{s^3} & $s \rightarrow 0$ \\
\frac{1}{2s^2} - \frac{3}{8s^6} + \bigO{s^{-10}} & $s \rightarrow \infty$
\end{cases*} \\
\frac{C}{\sigma^2} &=
\begin{cases*}
\frac{1}{2s} - \frac{1}{8}s + \bigO{s^3} & $s \rightarrow 0$ \\
\frac{1}{2s^2} - \frac{1}{4s^6} + \bigO{s^{-10}} & $s \rightarrow \infty$
\end{cases*}
& \zeta &=
\begin{cases*}
1 - \frac{1}{2}s + \frac{1}{8}s^2 + \bigO{s^3} & $s \rightarrow 0$ \\
\frac{1}{4^{1/4}s} - \frac{3 \cdot 4^{3/4}}{32 s^5} + \bigO{s^{-9}} & $s \rightarrow \infty$.
\end{cases*}
\label{eq:asympt}
\end{aligned}
\end{equation}
The general form of these is as expected. When $s \rightarrow 0$, we effectively remove the \gls{cfbg} from the cavity. This causes the pulse to be perpetually modulated, and so, the pulse's shape approaches a $\delta$ function, and therefore, $\sigma^2 \rightarrow 0$. Moreover, since $\zeta$ is the ratio of the amplitude of the pulse before and after dispersion, $\zeta \rightarrow 1$. In the opposite extreme, $s \rightarrow \infty$, the length / strength of the \gls{cfbg} approaches infinity---this causes the pulse to broaden greatly, while conserving its energy. Because of this, the variance approaches unity because the shape is entirely determined by the modulation function. Additionally, $\zeta \rightarrow 0$ because the pulse becomes infinitely wide, and thus, the amplitude becomes infinitesimally small. Due to the expansive nature, the chirp approaches zero because any chirp will be expanded away. \\

### 2019-07-12 Thesis/Appendices/Dispersion.tex
Finished second draft
Finished corrections

% !TeX root = ../Thesis.tex
%\chapter{Spread Due to Dispersion}
%\label{chap:disp}
The effect of dispersion can be computed analytically for input pulses using \eqref{eq:disp}. In the case of a Gaussian pulse, we make use of the transforms \cite{debnath, gradshteyn}
\begin{align*}
\FT{\textrm{e}^{-\eta T^2}} &= (2 \eta)^{-1/2}\textrm{e}^{-\omega^2/4\eta},& \FTi{\textrm{e}^{-\eta \omega^2}} &= (2 \eta)^{-1/2}\textrm{e}^{-T^2/4\eta}.
\end{align*}
From \eqref{eq:disp} we have that
\begin{align*}
D \left( \textrm{e}^{-\eta T^2} \right) &=\FTi{\textrm{e}^{i s^2 \omega^2} \FT{\textrm{e}^{-\eta T^2}}}, \\
&= (2 \eta)^{-1/2} \FTi{\exp \left( -\omega^2 \left( \frac{1}{4\eta} - i s^2 \right) \right)}, \\
&= (1 - 4 i \eta s^2)^{-1/2} \exp \left( -T^2 \frac{a}{1 - 4 i s^2 \eta} \right).
\end{align*}
For us, $\displaystyle \eta = \frac{1}{2} \frac{1 + i C}{\sigma^2}$; making this substitution yields
\begin{align*}
D(A_1) &= \left( 1 + \frac{2C s^2}{\sigma^2} - \frac{2s^2}{\sigma^2}i \right)^{-1/2} \exp \left( -T^2 \frac{1 + i C}{2\sigma^2 - 4 i s^2 (1 + i C)} \right).
\end{align*}
This can be greatly simplified by first rationalizing the denominators to give
\begin{align*}
D(A_1) &= \left( \frac{1 + \frac{2C s^2}{\sigma^2} + \frac{2s^2}{\sigma^2}i}{\left( 1 + \frac{2C s^2}{\sigma^2} \right)^2 + \left( \frac{2s^2}{\sigma^2} \right)^2} \right)^{1/2} \exp \left( -T^2 \frac{(1 + i C)(2\sigma^2 + 4 C s^2 + 4 i s^2)}{(2\sigma^2 + 4C s^2)^2 + 16s^4} \right),
\end{align*}
and then by writing in polar coordinates:
\begin{multline*}
D(A_1) = \left( \left( 1 + \frac{2C s^2}{\sigma^2} \right)^2 + \left( \frac{2s^2}{\sigma^2} \right)^2 \right)^{-1/4} \exp \left( \frac{1}{2} i \arctan \left( \frac{\frac{2s^2}{\sigma^2}}{1 + \frac{2C s^2}{\sigma^2}} \right) \right) \\
\times \exp \left( -T^2 \frac{\sigma^2 \left[ 1 + i \left( C + (1 + C^2) \frac{2s^2}{\sigma^2} \right) \right]}{2 \left[ (\sigma^2 + 2C s^2)^2 + 4s^4 \right]} \right).
\end{multline*}
Finally, this can be simplified further to
\begin{multline*}
D(A_1) = \sigma \left( \left( \sigma^2 + 2C s^2 \right)^2 + 4s^4 \right)^{-1/4} \exp \left( \frac{1}{2} i \arctan \left( \frac{2s^2}{\sigma^2 + 2C s^2} \right) \right) \\
\times \exp \left( -T^2 \frac{\sigma^2 \left[ 1 + i \left( C + (1 + C^2) \frac{2s^2}{\sigma^2} \right) \right]}{2 \left[ (\sigma^2 + 2C s^2)^2 + 4s^4 \right]} \right).
\end{multline*}
From this expression it is clear that at equilibrium
\begin{subequations}
\begin{align}
\label{eq:varout}
\widetilde{\sigma}^2 \sigma^2 &= \left( \sigma^2 + 2 C s^2 \right)^2 + 4s^4, \\
\label{eq:chirpout}
\widetilde{C} &= C + (1+C^2) \frac{2 s^2}{\sigma^2}, \\
\label{eq:phase}
\phi &= \frac{1}{2} \arctan \left( \frac{2s^2}{\sigma^2 + 2C s^2} \right), \\
\zeta &= \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2}.
\end{align}
\end{subequations}

The expressions for the chirp and variance can be verified with the well known relations \cite{agrawal2013, anderson, ferreira, silfvast}
\begin{align*}
\left( \frac{T_1}{T_0} \right)^2 &= \left( 1 + \frac{C \beta_2 z}{T_0^2} \right)^2 + \left( \frac{ \beta_2 z}{T_0^2} \right)^2,&
\widetilde{C} &= C + (1+C^2) \frac{\beta_2 z}{T_0^2}.
\end{align*}
Where, within our non-dimensionalization, $T_0 = \sigma T_M$, $T_1 = \widetilde{\sigma} T_M$, $z = L_D$, and $\beta_2 z T_0^{-2} = 2s^2\sigma^{-2}$. In addition to this, the expression for $\zeta$ can be validated using conservation of energy. Within the CFBG energy is conserved, therefore,
\begin{align*}
\int_{-\infty}^\infty |A_1|^2 \, \df T &= \int_{-\infty}^\infty |A_2|^2 \, \df T.
\end{align*}
Which, after substituting the expressions from Section \ref{sec:linear}, reduces to
\begin{align*}
h^2 P \int_{-\infty}^\infty \textrm{e}^{-T^2/\sigma^2} \, \df T &= h^2 P \zeta \int_{-\infty}^\infty \textrm{e}^{-T^2/\widetilde{\sigma}^2} \, \df T.
\end{align*}
These expressions are easily integrated to show that $\sqrt{\pi \sigma^2} = \sqrt{\pi \widetilde{\sigma}^2} \zeta^2$, and finally that
\begin{align*}
\zeta &= \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2}.
\end{align*}

>>>>

% !TeX root = ../Thesis.tex
%\chapter{Spread Due to Dispersion}
%\label{chap:disp}
The effect of dispersion can be computed analytically for input pulses using \eqref{eq:disp}. In the case of a Gaussian pulse, we make use of the transforms \cite{debnath, gradshteyn}
\begin{align*}
\FT{\textrm{e}^{-\eta T^2}} &= (2 \eta)^{-1/2}\textrm{e}^{-\omega^2/4\eta},& \FTi{\textrm{e}^{-\eta \omega^2}} &= (2 \eta)^{-1/2}\textrm{e}^{-T^2/4\eta}.
\end{align*}
From \eqref{eq:disp} we have that
\begin{align*}
D \left( \textrm{e}^{-\eta T^2} \right) &=\FTi{\textrm{e}^{i s^2 \omega^2} \FT{\textrm{e}^{-\eta T^2}}}, \\
&= (2 \eta)^{-1/2} \FTi{\exp \left( -\omega^2 \left( \frac{1}{4\eta} - i s^2 \right) \right)}, \\
&= (1 - 4 i \eta s^2)^{-1/2} \exp \left( -T^2 \frac{a}{1 - 4 i s^2 \eta} \right).
\end{align*}
For us, $\displaystyle \eta = \frac{1}{2} \frac{1 + i C}{\sigma^2}$; making this substitution yields
\begin{align*}
D(A_1) &= \left( 1 + \frac{2C s^2}{\sigma^2} - \frac{2s^2}{\sigma^2}i \right)^{-1/2} \exp \left( -T^2 \frac{1 + i C}{2\sigma^2 - 4 i s^2 (1 + i C)} \right).
\end{align*}
This can be greatly simplified by first rationalizing the denominators to give
\begin{align*}
D(A_1) &= \left( \frac{1 + \frac{2C s^2}{\sigma^2} + \frac{2s^2}{\sigma^2}i}{\left( 1 + \frac{2C s^2}{\sigma^2} \right)^2 + \left( \frac{2s^2}{\sigma^2} \right)^2} \right)^{1/2} \exp \left( -T^2 \frac{(1 + i C)(2\sigma^2 + 4 C s^2 + 4 i s^2)}{(2\sigma^2 + 4C s^2)^2 + 16s^4} \right).
\end{align*}
Finally, this can be simplified further to\footnote{For $a, b \in \mathbb{R}$ $\displaystyle (a + bi)^{1/2} = (a^2 + b^2)^{1/4} \exp \left( \frac{1}{2}i \arctan \left( \frac{b}{a} \right) \right)$.}
\begin{multline*}
D(A_1) = \sigma \left( \left( \sigma^2 + 2C s^2 \right)^2 + 4s^4 \right)^{-1/4} \exp \left( \frac{1}{2} i \arctan \left( \frac{2s^2}{\sigma^2 + 2C s^2} \right) \right) \\
\times \exp \left( -T^2 \frac{\sigma^2 \left[ 1 + i \left( C + (1 + C^2) \frac{2s^2}{\sigma^2} \right) \right]}{2 \left[ (\sigma^2 + 2C s^2)^2 + 4s^4 \right]} \right).
\end{multline*}
From this expression it is clear that at equilibrium
\begin{subequations}
\begin{align}
\label{eq:varout}
\widetilde{\sigma}^2 \sigma^2 &= \left( \sigma^2 + 2 C s^2 \right)^2 + 4s^4, \\
\label{eq:chirpout}
\widetilde{C} &= C + (1+C^2) \frac{2 s^2}{\sigma^2}, \\
\label{eq:phase}
\phi &= \frac{1}{2} \arctan \left( \frac{2s^2}{\sigma^2 + 2C s^2} \right), \\
\zeta &= \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2}.
\end{align}
\end{subequations}

The expressions for the chirp and variance can be verified by comparing to the dimensional equivalents from the literature \cite{agrawal2013, anderson, ferreira, silfvast}. One finds
\begin{align*}
\left( \frac{T_1}{T_0} \right)^2 &= \left( 1 + \frac{C \beta_2 z}{T_0^2} \right)^2 + \left( \frac{ \beta_2 z}{T_0^2} \right)^2,&
\widetilde{C} &= C + (1+C^2) \frac{\beta_2 z}{T_0^2},
\end{align*}
with the conversions $T_0 = \sigma T_M$, $T_1 = \widetilde{\sigma} T_M$, and $\beta_2 L_D T_0^{-2} = 2s^2\sigma^{-2}$. In addition to this, the expression for $\zeta$ can be validated using conservation of energy. Within the \gls{cfbg} energy is conserved, therefore,
\begin{align*}
\int_{-\infty}^\infty |A_1|^2 \, \df T &= \int_{-\infty}^\infty |A_2|^2 \, \df T.
\end{align*}
After substituting the expressions, reduces to
\begin{align*}
h^2 P \int_{-\infty}^\infty \textrm{e}^{-T^2/\sigma^2} \, \df T &= h^2 P \zeta \int_{-\infty}^\infty \textrm{e}^{-T^2/\widetilde{\sigma}^2} \, \df T.
\end{align*}
These expressions are easily integrated to show that $\sqrt{\pi \sigma^2} = \sqrt{\pi \widetilde{\sigma}^2} \zeta^2$, and finally that
\begin{align*}
\zeta &= \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2}.
\end{align*}
